\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in, right=0.6in, top=0.55in, bottom=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontenc}
\usepackage{lmodern}

\pagenumbering{gobble}

% Color for section rules and accents
\definecolor{darkblue}{RGB}{0, 51, 102}

% Section formatting — small caps label, full-width rule
\titleformat{\section}
  {\large\bfseries\color{darkblue}}{}{0em}{}
  [\color{darkblue}\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Compact list settings
\setlist[itemize]{
  noitemsep,
  topsep=2pt,
  partopsep=0pt,
  parsep=0pt,
  leftmargin=1.2em,
  label=\textbullet
}

% Hyperlink style
\hypersetup{
  colorlinks=false,
  urlbordercolor=darkblue
}

\begin{document}

% ─────────────────────────── HEADER ───────────────────────────
\begin{center}
  {\LARGE \textbf{Alex Example}} \\[4pt]
  {\small
    Example City, State, Country \quad\textbar\quad
    \href{mailto:alex@example.com}{alex@example.com} \quad\textbar\quad
    +1-555-010-1234 \\[2pt]
    \href{https://www.linkedin.com/in/alex-example}{linkedin.com/in/alex-example} \quad\textbar\quad
    \href{https://github.com/alex-example}{github.com/alex-example}
  }
\end{center}




% ─────────────────────────── EXPERIENCE ───────────────────────────
\section*{Professional Experience}

% --- Job 1 ---
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Senslyze} & \textit{Aug 2025 – Present}
\end{tabularx}
\textit{Software Development Engineer}

\begin{itemize}
  \item Designed and deployed production-grade WhatsApp-native AI systems with secure webhooks, encrypted Flow endpoints (RSA/AES), and scalable backend services.
  \item Built end-to-end RAG pipelines (PDF → chunking → embeddings → Qdrant retrieval) enabling grounded, context-aware responses with optimized latency.
  \item Engineered hybrid conversational systems combining deterministic state machines with LLM-based structured NLU.
  \item Orchestrated multimodal AI workflows (STT → NLU → reasoning → TTS) enabling voice-first interactions.
  \item Implemented vision-based validation using multimodal LLMs for strict JSON outputs (accept/reject + scoring).
  \item Developed LLM routing pipelines using OpenAI-compatible APIs, OpenRouter, and Gemini fallback strategies.
  \item Built a Flow Builder platform for visualizing and managing conversational workflows.
  \item Applied schema validation (Zod) and structured prompting to improve reliability and reduce hallucination.
\end{itemize}

\vspace{4pt}

% --- Job 2 ---
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Dinosys Infotech Pvt Ltd} & \textit{Jul 2024 – Mar 2025}
\end{tabularx}
\textit{Software Developer}

\begin{itemize}
  \item Developed OSINT automation tools for law enforcement using Python and Selenium.
  \item Built backend pipelines for data extraction, normalization, and analysis.
  \item Optimized scraping workflows using parallel execution to improve efficiency.
\end{itemize}

% ─────────────────────────── PROJECTS ───────────────────────────
\section*{Projects}



% --- Project 1 ---
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Refaktr AI} &
\end{tabularx}
\textit{VS Code Extension, TypeScript/Node.js, Express, ts-morph, Graph-based Analysis, LLM Planning}
\begin{itemize}
  \item Designed an AI-assisted refactoring system that converts codebases into dependency graphs and generates structured refactor plans from user intent.
  \item Executed safe code transformations using AST-based edits, avoiding regex-based risks and ensuring maintainability.
  \item Built step-wise execution pipeline with validation hooks (type-check, build, tests) to ensure reliable and reviewable refactors.
\end{itemize}

\vspace{4pt}

% --- Project 2 ---
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{AI Document Analyzer} &
  \href{https://example.com/demo}{\small Live} \;|\;
  \href{https://example.com/demo-video}{\small Demo} \;|\;
  \href{https://github.com/alex-example/sample-project}{\small GitHub}
\end{tabularx}
\textit{React, TypeScript, FastAPI, Python, PostgreSQL, LangChain, Gemini, Docker}
\begin{itemize}
  \item Built an AI-powered platform for document analysis, summarization, and RAG-based Q\&A with a containerized stack.
\end{itemize}

\vspace{4pt}

% --- Project 3 ---
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{DevPilotAI} &
  \href{https://github.com/alex-example/devpilot-ai}{\small GitHub}
\end{tabularx}
\textit{Next.js, TypeScript, Express, Gemini, LangChain, Qdrant}
\begin{itemize}
  \item Built an AI development assistant with RAG-based code querying, architecture generation, and real-time streaming outputs.
\end{itemize}

% ─────────────────────────── SKILLS ───────────────────────────
\section*{Technical Skills}

\newsavebox{\skillsbox}
\begin{lrbox}{\skillsbox}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{2.8cm} X@{}}
  AI / ML          & RAG, NLP, Prompt Engineering, Multimodal AI (Vision + Voice), Embeddings, Vector DB (Qdrant, FAISS) \\
  LLM Systems      & OpenAI APIs, OpenRouter, Gemini, LangChain, LLM Routing, Tool Calling, AI Orchestration \\
  Backend          & Node.js, Express, FastAPI, Flask, Bun, Hono, REST APIs, Webhooks \\
  Frontend         & React.js, Next.js, TypeScript \\
  Databases        & PostgreSQL, Prisma, SQLite \\
  DevOps           & Docker, Git, Postman, Linux, AWS \\
  Core CS          & DSA, OS, DBMS, CN, OOP \\
\end{tabularx}
\end{lrbox}
\usebox{\skillsbox}

% ─────────────────────────── EDUCATION ───────────────────────────
\section*{Education}

\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{B.E. in Computer Science and Engineering} & \textbf{June 2025} \\
  Government College of Engineering, Chandrapur & CGPA: \textbf{8.94 / 10.00}
\end{tabularx}

\end{document}
