\documentclass[11pt,letterpaper]{article}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{fontawesome5}
\usepackage{xcolor}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\pagestyle{empty}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape Yash Anghan} \\ \vspace{2pt}
\small \raisebox{-0.1\height}\faEnvelope\ \href{mailto:yashanghan97@gmail.com}{yashanghan97@gmail.com} ~
\raisebox{-0.1\height}\faPhone\ +1 (437) 290-2005 ~
\href{https://www.linkedin.com/in/yash-aiautomation/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Linkedin}} ~
\href{https://github.com/yash-ai-automation}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
\vspace{-8pt}
\end{center}

\vspace{-17pt}
\noindent\rule{\textwidth}{0.4pt}
\vspace{4pt}

%----------DATE \& ADDRESS----------
May 13, 2026

Hiring Manager \\
Scribd, Inc. \\
Toronto, ON

\textbf{Re: Software Engineer II (Backend + Data pipelines)}

%----------BODY----------
Dear Hiring Manager,

I am applying for the Software Engineer II (Backend + Data pipelines) role at Scribd, Inc. to bring 6+ years of enterprise engineering at Bell Canada and Morningstar---where I shipped production systems handling 10M+ daily transactions---into your ML Data Engineering team. At Morningstar I engineered Python \textbf{data pipelines} for AI-powered \textbf{metadata extraction} that cut manual analyst review time by 65\% across 12K monthly fund documents. That same enterprise discipline now drives my AI automation work, and I am eager to apply it to Scribd's content-metadata problem at global scale.

Your team processes hundreds of millions of documents and billions of images using \textbf{LLMs}, distributed systems on AWS (ECS, Lambda, Sagemaker), Terraform-as-code, and Spark/Databricks workloads---every one of those layers maps directly to my day-to-day toolset. At Morningstar I built RAG and \textbf{generative AI} pipelines on AWS Sagemaker provisioned with Terraform, supporting 25K+ daily prediction requests at sub-200ms latency for analyst-facing research surfaces. At Bell I developed \textbf{microservices} and \textbf{distributed systems} that handled 45K daily transactions with 99.9\% uptime, plus REST APIs serving 850K active subscribers with sub-100ms response times. I have also implemented automated validation and monitoring workflows that surface anomalies across regulated SEC filing data---directly relevant to the data accuracy, integrity, and quality requirements in your role description. Together these proof points map cleanly onto designing, building, and optimizing the metadata-enrichment pipelines you are hiring for.

Scribd, Slideshare, Everand, and Fable together advance the mission of moving billions of readers from access into insight, application, and expertise---and metadata enrichment is the connective tissue that makes that promise real. The opportunity to ship cutting-edge LLM-powered classification, summarization, and extraction into pipelines that touch hundreds of millions of documents is exactly the scale of impact I want my next role to have. The team's mix of applied research, ML engineering, and cross-functional product collaboration mirrors how I have shipped GenAI systems before at Morningstar, and lets me contribute on day one.

I would welcome the chance to discuss how my backend engineering background and AI automation expertise can accelerate Scribd's metadata-enrichment roadmap. Thank you for considering my application.

Sincerely,

Yash Anghan

\end{document}
